\documentclass[10pt]{extarticle}
\usepackage[margin = 1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx, fancyhdr, lipsum}
\usepackage{amsfonts, amssymb}
\usepackage{amsmath, amsthm, lipsum, mathtools}
\usepackage{xparse, tikz, multicol, enumitem, pgfplots}
\usepackage{algorithm, algpseudocode}
\usepackage{tcolorbox}
\tcbuselibrary{theorems, breakable, skins}
\usepackage{hyperref}
\usepackage{stickstootext}
\usepackage[stickstoo,vvarbb]{newtxmath}
\usepackage[framemethod = TikZ]{mdframed}
\usetikzlibrary{shadows, shapes.geometric, positioning, arrows.meta}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}
\pgfplotsset{compat=newest}

\input{base-tex-files/commands.tex}
\input{base-tex-files/exercise_macros.tex}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={DNF Exercises},
    }

\tikzset{
    lattice edge/.style = {draw, -},
}

\tikzset{
    u/.style = {lattice edge, to path={(\tikztostart) -- (\tikztotarget.south)\tikztonodes}},
    uu/.style = {lattice edge, to path={(\tikztostart.north) -- (\tikztotarget)\tikztonodes}},
}

\urlstyle{same}

\pagecolor{pagecolor!50}

\pagestyle{fancy}
\fancyhead{}
\fancyhead[R]{\rightmark}
\setlength{\headheight}{14pt}
\addtolength{\topmargin}{-0.5pt}

\title{Solutions to Dummit \& Foote's Abstract Algebra $3^{\text{rd}}$ Edition}
\author{JR}
\date{October $27^{\text{th}}$, 2025}

\setlength{\jot}{2pt}
\setlength{\parindent}{0.75cm}

\includeonly{exercises/chap1ex}

\begin{document}

\maketitle

\tableofcontents

\newpage

\section*{Preface}
\addcontentsline{toc}{section}{\protect\numberline{}Preface}

This is a collection of solutions to the exercises in Dummit and Foote's \textit{Abstract Algebra}, $3^{\text{rd}}$ edition, written as I worked through the book to serve as a reference for myself and others studying abstract algebra. While I have made every effort to ensure correctness, I cannot guarantee the solutions are error-free; if you find any mistakes, please feel free to contact me.

I have formatted the solutions clearly and consistently using \LaTeX, with each chapter's exercises in separate files for better organization. The solutions employ only techniques accessible to advanced undergraduates or beginning graduate students, consistent with the textbook's intended audience. As context, I hold a bachelor's degree in mathematics but have not pursued graduate studies, so my background is primarily at the undergraduate level.

Exercises are numbered by chapter and section. For clarity: ``remark'' denotes Dummit and Foote's expository remarks, ``hints'' refers to their exercise hints (which vary in detail), and ``A/N'' marks my author's notes with additional insights, alternative approaches, or clarifications intended to help readers develop a deeper understanding of the material.

\begin{exercise}
    Example exercise.
\end{exercise}

I have marked certain exercises as ``special exercises'' because they are particularly important, interesting, or involve complex solutions. These are highlighted in a distinct color with a more visually appealing format. Since the results from these exercises frequently appear in later chapters, I have provided more detailed solutions to help readers deepen their understanding of the material.

\begin{specialexercise}[Example Special Exercise]
    Example special exercise.
\end{specialexercise}

Many thanks to the authors, David S. Dummit and Richard M. Foote, for writing such an excellent textbook that has been a valuable resource for my recreational studies in abstract algebra. I've received requests on Reddit for individuals to assist me in completing this project, but at this time I prefer to work on it independently. However, I welcome feedback and suggestions from anyone who is interested in contributing to the project in the future.

\newpage

\section*{Contributors}
\addcontentsline{toc}{section}{\protect\numberline{}Contributors}

As of now, I am independently forming solutions to each exercise myself. However, I welcome any corrections, suggestions, or slicker solutions from others. A (growing) list of contributors will be maintained here. If you'd like to contact me, please reach out on Reddit at \href{https://www.reddit.com/user/ansv9a8fdh3/}{my profile} or via Discord, where my username is blanketism. Thank you to everyone who decided to take time out of their busy lives to contribute to this project. I appreciate your help in making it better for everyone.
\begin{itemize}
    \item greysonbowser
    \item coolempire93
\end{itemize}

\include{exercises/chap0ex}
\include{exercises/chap1ex}
\include{exercises/chap2ex}
\include{exercises/chap3ex}
\include{exercises/chap4ex}
\include{exercises/chap5ex}

\end{document}