\section*{Preface}
\addcontentsline{toc}{section}{\protect\numberline{}Preface}

This collection contains solutions to the exercises in David S. Dummit and Richard M. Foote's \textit{Abstract Algebra}, Third Edition—a comprehensive graduate-level text that has become a standard reference in the field. I have worked through these problems over time to deepen my understanding of the material and to create a resource for others studying abstract algebra. While these solutions are written with care and rigor, they are not guaranteed to be error-free; if you discover mistakes or have suggestions for improvement, I welcome corrections.

Solutions are organized by chapter and section, mirroring the structure of the textbook. Within each section, exercises are presented in the order they appear in the book. Each solution aims to be self-contained but frequently references prior results; when a proof depends heavily on another exercise or theorem, I note this explicitly.
\begin{exercise}
    Most problems in the book are presented in the standard exercise environment. These exercises are typically routine and don't require advanced mathematical insight beyond the techniques and concepts introduced in the text.
\end{exercise}
\begin{specialexercise}
    Problems in the ``special exercise'' environment are included because they are particularly important, instructive, or deep. Some are challenging in their proof techniques or conceptual demands; others are simple but illustrate key ideas fundamental to the overall text. These exercises deepen understanding and often provide insight into material developed later in the book.
\end{specialexercise}
\vspace{1ex}
This is an ongoing project. As I work through the text, I refine earlier solutions and add new ones. While I strive for mathematical correctness, errors may remain--particularly in computational problems or long proofs. I encourage you to read critically, verify claims, and develop your own solutions. The goal is not to provide answers to be memorized, but to illustrate good problem-solving techniques and deepen your understanding of abstract algebra.

I am completing this project independently at my own pace. That said, I genuinely welcome corrections, suggestions, and alternative solutions from the community. If you find errors, have ideas for improvement, or wish to contribute, please open an issue or submit a pull request on GitHub. You may also reach out directly via Reddit or Discord with feedback or discussion. I appreciate the interest in helping this project grow and remain open to community involvement.

My deepest thanks to David S. Dummit and Richard M. Foote for writing \textit{Abstract Algebra}. Their exposition is remarkably clear, their choice of exercises is thoughtful and comprehensive, and their book has been instrumental in my mathematical development. Many of these solutions exist because of the beauty and depth of their presentation.

Finally, I'd like to take a moment and thank the broader mathematics community for maintaining a culture of shared knowledge. The practice of working through textbooks and sharing solutions has a long and valuable tradition, and I am grateful to everyone who contributes to this collective effort. I hope that this project, in its small way, adds to that tradition and proves useful to others in their study of abstract algebra. Please enjoy!